---
title: "ggstatsplot"
author: "ylchen"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F,message = F,collapse=TRUE)
```

* ggstatsplot主要用途：可视化+统计分析

* 在统计学分析方面：目前它支持最常见的统计测试类型：t-test / anova，非参数，相关性分析，列联表分析和回归分析。

* 集中趋势测量方法Central tendency measure
Parametric	mean 正态分布
Non-parametric	median 非正态
Robust	trimmed mean 相关性
Bayesian	MAP (maximum a posteriori probability) estimate 最大后验估计

* 而在图片输出方面：
  （1）小提琴图（用于不同组之间连续数据分析）；
  （2）饼图（用于分类数据的分布检验）；
  （3）条形图（用于分类数据的分布检验）；
  （4）散点图（用于两个变量之间的相关性分析）；
  （5）相关矩阵（用于多个变量之间的相关性分析）；
  （6）直方图和点图/图表（关于分布的假设检验）；
  （7）点须图（用于回归模型）。

* 参考：https://indrajeetpatil.github.io/ggstatsplot/index.html

```{r}
#install.packages("ggstatsplot")
library(ggstatsplot)
```

# 一、ggbetweenstats 多组间的均数比较

* 创建小提琴图、盒子图或两组或条件之间比较的混合图
* 正态异方差（特别是样本数不等的情况下）用Welch's ANOVA


```{r}
# for reproducibility
set.seed(123)
head(iris)

# plot
ggbetweenstats(
  data = iris,
  x = Species,
  y = Sepal.Length,
  title = "Distribution of sepal length across Iris species"
)
```

# 二、ggwithinstats 重复测量设计

* 用法与ggbetweenstats相似，添加了路径连接
* 配对检验

```{r}
# for reproducibility and data
set.seed(123)
library(WRS2) # for data
library(afex) # to run anova
#BiocManager::install('ggthemes')
head(WineTasting)
table(WineTasting$Taster) #22对
# plot
ggwithinstats(
  data = WineTasting,
  x = Wine,
  y = Taste,
  title = "Wine tasting",
  caption = "Data source: `WRS2` R package",
  ggtheme = ggthemes::theme_fivethirtyeight()
)
```

# 三、gghistostats 直方图
* 观察某连续变量分布情况
* 与固定值test.value进行单样本t检验

```{r}
# for reproducibility
set.seed(123)

# plot
gghistostats(
  data = ggplot2::msleep, # dataframe from which variable is to be taken
  x = awake, # numeric variable whose distribution is of interest
  title = "Amount of time spent awake", # title for the plot
  caption = substitute(paste(italic("Source: "), "Mammalian sleep data set")),
  test.value = 12, # default value is 0
  normal.curve = TRUE, # 发布曲线
  normal.curve.args = list(color = "red", size = 1),
  binwidth = 1, # 组距
  ggtheme = hrbrthemes::theme_ipsum_tw(),
  bf.message = FALSE ## 去除贝叶斯相关的统计值
)
```

# 四、ggdotplotstats 点图
* type = "robust" :Bootstrap-t method for one-sample test
* https://zhuanlan.zhihu.com/p/41099219

```{r}
# for reproducibility
set.seed(123)

# plot
ggdotplotstats(
  data = dplyr::filter(.data = gapminder::gapminder, continent == "Asia"),
  y = country,
  x = lifeExp,
  test.value = 55,
  type = "robust",
  title = "Distribution of life expectancy in Asian continent",
  xlab = "Life expectancy",
  caption = substitute(
    paste(
      italic("Source"),
      ": Gapminder dataset from https://www.gapminder.org/"
    )
  )
)
```


# 五、ggscatterstats 散点图

1. 边缘分布类型marginal.type：
  * histograms
  * boxplots
  * density
  * violin
  * densigram (density + histogram)
  
2. 假设检验类型type：
  * Parametric	Pearson’s correlation coefficient
  * Non-parametric	Spearman’s rank correlation coefficient
  * Robust	Winsorized Pearson correlation coefficient
  * Bayesian	Pearson’s correlation coefficient
  
3. 去除贝叶斯相关的统计值bf.message = FALSE 

```{r}
# for reproducibility
set.seed(123)
data <- dplyr::filter(movies_long, genre == "Action")
head(data)
# plot
ggscatterstats(
  data = data,
  x = budget,
  y = rating,
  type = "robust", # Winsorized Pearson correlation coefficient
  xlab = "Movie budget (in million/ US$)", # label for x axis
  ylab = "IMDB rating", # label for y axis
  label.var = title, # 标注点
  label.expression = rating < 5 & budget > 100, # 标注点的条件
  title = "Movie budget and IMDB rating (action)", # title text for the plot
  caption = expression(paste(italic("Note"), ": IMDB stands for Internet Movie DataBase")),#右下方注释
  ggtheme = hrbrthemes::theme_ipsum_ps(), # choosing a different theme
  # turn off `ggstatsplot` theme layer
  marginal.type = "densigram", # 边缘分布
  xfill = "pink", # color fill for x-axis marginal distribution
  yfill = "#009E73" # color fill for y-axis marginal distribution
)
```

# 六、ggcorrmat 相关性图

```{r}
# for reproducibility
set.seed(123)

# as a default this function outputs a correlation matrix plot
ggcorrmat(
  data = ggplot2::msleep,
  type = "Parametric",
  colors = c("#B2182B", "white", "#4D4D4D"),
  title = "Correlalogram for mammals sleep dataset",
  subtitle = "sleep units: hours; weight units: kilograms"
)

# output = "dataframe" 具体参数值
head(
  ggcorrmat(
  data = ggplot2::msleep,
  type = "Parametric",
  colors = c("#B2182B", "white", "#4D4D4D"),
  title = "Correlalogram for mammals sleep dataset",
  subtitle = "sleep units: hours; weight units: kilograms",
  output = "dataframe"
))
```

# 七、ggpiestats 饼图

```{r}
# for reproducibility
set.seed(123)

# plot
ggpiestats(
  data = mtcars,
  x = am,
  y = cyl,
  package = "wesanderson",
  palette = "Royal1", # 调色板
  title = "Dataset: Motor Trend Car Road Tests", # title for the plot
  legend.title = "Transmission", # title for the legend
  caption = substitute(paste(italic("Source"), ": 1974 Motor Trend US magazine"))
)
```

# 八、ggbarstats 柱状图

```{r}
# for reproducibility
set.seed(123)
library(ggplot2)

# plot
ggbarstats(
  data = movies_long,
  x = mpaa,
  y = genre,
  title = "MPAA Ratings by Genre",
  xlab = "movie genre",
  legend.title = "MPAA rating",
  ggtheme = hrbrthemes::theme_ipsum_pub(),
  palette = "Set2"
)
```

